---
title: "Week 4 Submission"
author: "Jayesh Samant"
date: "January 25, 2017"
output: ioslides_presentation
---

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(datasets)
library(ggplot2)
library(reshape2)
library(dplyr)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objective

The Objective of this application is to diagramatically display the growth of phone usage in the different geographic regions between 1951 and 1961.

For this purpose we use the WorldPhones dataset.
```{r}
WorldPhones
```

WorldPhones provides information about the number of phones in the different regions and years in a matrix form.

## How to Use

The Shiny app can be accessed here - http://jayeshs81.shinyapps.io/Week4Submission

Our Shiny app, allows you to plot the # of phone depending on which years and regions you are interested in. 

To use the Shiny app:  
- Select the Region(s) which you want to display in the plot   
- Select the Year(s) which you want to display in the plot

On changing the selection of the region or the year check boxes a new plot is created in the main panel.

## Displayed Plot

The plot displat a dodged bar plot of the number of phones for each of the selected years and region. A plot for all regions and years selected is shown below.

```{r, echo=FALSE}
# Format the WorldPhones data for processing
melted <- melt(WorldPhones)
names(melted) <- c("Year", "Region", "Count")
melted$Year <- as.factor(melted$Year)
    
# Plot the selected data
g <- ggplot(data = melted, aes(x = Year, y = Count))
g <- g + geom_bar(aes(fill = Region), position = "dodge", stat = "identity")
g <- g + xlab("Year") + ylab("# of Phones") 
g
```

## Hope you enjoy the app!!